\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-12 proof-sgd.tex
Finishing part (ii) of SGD theorem convergence

This proof requires somewhat more techinicality than the first part of the
theorem, including a brief detour into local asymptotic normality theory,
regular estimators, and quadratic-mean
differentiability~\cite[cf.]{VanDerVaart98}.
We begin by recalling some of these concepts.
\begin{definition}
  \label{definition:regular-estimator}
  A sequence of estimators $T_n$ for a parameter $\theta$ in the parametric
  family $\{P_\theta\}_{\theta \in \Theta}$ is \emph{regular at $\theta$} if
  there exists a distribution $Q$ such that for all bounded sequence
  $h_n$,
  \begin{equation*}
    \sqrt{n}(T_n - (\theta + h_n / \sqrt{n}))
    \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}}
    Q.
  \end{equation*}
\end{definition}
\begin{definition}
  \label{definition:qmd}
  Let $\{P_\theta\}_{\theta \in \Theta}$ have densities $p_\theta$
  with respect to a base measure $\mu$. The family
  is \emph{quadratic mean differentiable} (QMD) at
  $\theta$ with score $\score_\theta$ if
  \begin{equation}
    \label{eqn:qmd}
    \int \left(\sqrt{p_{\theta + h}} - \sqrt{p_\theta}
    - \half h^\top \score_\theta\sqrt{p_\theta} \right)^2 d\mu
    = o(\norm{h}^2)
  \end{equation}
  as $h \to 0$.
\end{definition}
\begin{definition}
  \label{definition:lan}
  A family of distributions $\{P_\theta\}_{\theta \in \Theta}$ is
  \emph{locally asymptotically normal with information matrix $I_\theta$} (LAN)
  at
  $\theta$ if there exists a sequence of random vectors $Z_n$ such that for
  all $h_n \to h$,
  \begin{equation*}
    \sum_{i = 1}^n \log \frac{dP_{\theta + h_n/\sqrt{n}}}{dP_\theta}
    (X_1, \ldots, X_n)
    = h^\top Z_n - \half h^\top I_\theta h + o_P(1)
  \end{equation*}
  where $Z_n \cd \normal(0, I_\theta)$ under $P_\theta$, where
  $X_i \simiid P_\theta$.
\end{definition}

These three definitions are linked in our case by a few important results.
First~\cite[Theorem 7.2]{VanDerVaart98}, if $\{P_\theta\}$ is QMD
(Def.~\ref{definition:qmd}) at the point $\theta$, then it is locally
asymptotically normal with $Z_n = \frac{1}{\sqrt{n}} \sum_{i = 1}^n
\score_\theta(X_i)$ and information matrix $I_\theta =
\E_\theta[\score_\theta \score_\theta^\top]$. Moreover, in any family
$\{P_\theta\}$ that is LAN (Def.~\ref{definition:lan}) at $\theta$, if $T_n$
is a regular estimator (Def.~\ref{definition:regular-estimator}) at $\theta$
with limiting distribution $Q$, then for any bounded, symmetric,
quasi-convex loss $L$ and $c < \infty$,
\begin{equation*}
  \limsup_n \sup_{\norm{h} \le c}
  \E_{P_{\theta + h/\sqrt{n}}}
  \left[L(\sqrt{n}(T_n - \theta - h / \sqrt{n}))\right]
  = \E[L(W)] ~~ \mbox{for~}W \sim Q
\end{equation*}
(see Beran~\cite{beran1995role}, Eq.~(4.2)).
%
Thus, we show two results: first, that
that the family $\{P_\theta\}$ of distributions
defined by the shifted densities $\{f(\cdot - \theta)\}_{\theta \in \R}$
is quadratic-mean-differentiable at any $\theta$,
and second, that $\bar{\theta}_n$ is regular and
asymptotically normal.
The combination evidently gives the theorem.

First, we have the following lemma, somewhat more general than we need, but
whose proof we provide in Sec.~\ref{sec:proof-qmd}.
\begin{lemma}[Extension of \cite{VanDerVaart98}, Lemma 7.6]
  \label{lemma:qmd}
  Let $p_\theta$ be a density with respect to $\mu$,
  and assume that $\theta \mapsto s_\theta(x) \defeq \sqrt{p_\theta(x)}$
  is absolutely continuous for all $x$. Let
  $\dot{p}_\theta(x) = \nabla_\theta p_\theta(x)$ (when it exists),
  and assume that
  \begin{equation*}
    \mu(\{x : \dot{p}_\theta(x) ~ \mbox{fails~to~exist}\}) = 0.
  \end{equation*}
  Assume that $I_\theta \defeq \E_{P_\theta}[\dot{p}_\theta
    \dot{p}_\theta^\top / p_\theta^2]$ is continuous at $\theta_0$. Then
  $P_\theta$ is QMD (Definition~\ref{definition:qmd}) at $\theta = \theta_0$
  with $\score_\theta = \dot{p}_\theta / p_\theta$.
\end{lemma}

We first show that the estimator $\bar{\theta}_n$ is regular in the
following sense: For $\theta \in \Theta$, a sequence $h_n \to h \in \R$ and
$n$ large enough that $\theta + h_n /\sqrt{n} \in \Theta$, let
$P_{\theta,n}$ be a product probability measure on $\R^n$ distributed
i.i.d.\ with density
$f(x - \theta - h_n/\sqrt{n})$. Then
\begin{align}
  \label{eqn:sgd-median-regular}
  \sqrt{n}\left( \bar{\theta}_n - \theta\right)
  \mathop{\cd}_{\Prob_{\theta,n}}
  \normal\left( h,\frac{1}{4 f(\theta)^2}\right),
\end{align}
under $\Prob_{\theta,n}$. To show the convergence~\eqref{eqn:sgd-median-regular} we
use the following refinement of Corollary~\ref{corollary:polyak-juditsky},
whose proof we defer to Section~\ref{proof:normal-expansion}.
%
\begin{corollary}
  \label{corollary:normal-expansion}
  Set $\Delta_i = \theta_i - \theta$ and $\bar{\Delta}_i = \frac{1}{n}
  \sum_{i=1}^n \Delta_i$. Let the conditions of
  Corollary~\ref{corollary:polyak-juditsky} hold, and additionally
  assume the local smoothness condition that there exist
  $0 < \lambda \le 1$ and $K < \infty$ such that
  \begin{equation}
    \label{eqn:additional-local-smooth}
    \E[|\varphi(x + Z) - \varphi(Z)|^2]
    \le K (|x|^\lambda + x^2).
  \end{equation}
  Then
  \begin{enumerate}[(i)]
  \item \label{item:regularity}
    The sequence $\Delta_i$ is regular, that is,
    \begin{equation}
      \sqrt{n} \bar{\Delta}_n
      = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)
      + o_{P,n}(1).
      \label{eq:normal_expansion_lem}
    \end{equation}
  \item \label{item:apply-le-cam} Let $Z_i$ as in
    Corollary~\ref{corollary:polyak-juditsky} have absolutely continuous
    density $p$ with median $0$, define $\score_h(z) = \frac{p'(z - h)}{p(z
      - h)}$, and assume that $I_h \defeq \E_\theta[\score_h(Z)^2]$ is
    continuous in $h$ near 0.  Then for any converging sequence $h_n \to h$,
    \begin{equation*}
      \sqrt{n} \bar{\Delta}_n
      \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}^n}
      \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
      , \frac{\chi(0)}{\psi'^2(0)} \right).
    \end{equation*}
  \end{enumerate}
\end{corollary}

We now verify that the setting of Theorem~\ref{thm:sgd} satisfies the
conditions of Corollary~\ref{corollary:polyak-juditsky}. First,
we have the obvious fact that
\begin{equation*}
  |\sgn(z) - \sgn(x + z)|
  \le 2 \cdot \indic{|x| \ge |z|}.
\end{equation*}
Recalling our w.l.o.g.\ assumption that $\theta = \mbox{med}(X) = 0$,
for $\varphi(z) = \sgn(z)$, and $Z = X - \theta = X$ we have
\begin{align*}
  \ex{ \left| \varphi(Z) - \varphi(x + Z) \right| }
  \leq 2 \Prob\left( |Z_1| \le |x|  \right)
  \le 2 f(0) |x| + \lip(f) x^2
\end{align*}
for $x$ near 0, where $\lip(f)$ is the Lipschitz constant of $f$ near
its median. For large $x$ we always have
$\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that
condition~\eqref{eqn:additional-local-smooth} holds.
In addition, we have
\begin{equation*}
  \int_{\R} \varphi(x) f'(x ) dx
  = \int_{\R} \sgn(x) f'(x ) dx =
  \int_0^\infty f'(x ) dx
  - \int_{-\infty}^0 f'(x )
  = -2 f(0) = -\psi'(0).
\end{equation*}
Corollary~\ref{corollary:normal-expansion}
now implies the convergence \eqref{eqn:sgd-median-regular}.

With the convergence~\eqref{eqn:sgd-median-regular},
the limiting efficiency estimate~\eqref{eq:attaining_LAM} is straightforward.
Indeed, the limiting distribution~\eqref{eqn:sgd-median-regular}
guarantees that $\bar{\theta}_n$ is a regular estimator,

Under the assumption that $f(x)$ is continuously differentiable with a finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \N}$ is differentiable in quadratic mean \cite[Exm. 7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
\begin{equation*}
\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
\end{equation*}
where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. The proof is concluded since any regular estimator in LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}.

\subsubsection*{Proof of (iii)}
%In order to prove part (ii) of Theorem~\ref{thm:sgd} 
Consider the following result from \cite{polyak1990new}:
\begin{thm}{\cite[Thm. 2]{polyak1990new}} \label{thm:polyak_new}
Let
\begin{align} \label{eq:polyak_new_measurements}
\begin{cases}
U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
\bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
\end{cases}
\end{align}
Assume that the function $g(x)$ is twice differentiable with a strictly
positive and uniformly bounded second derivative. In particular, $g(x)$ is
convex with a unique minimizer $x^\star \in \R$. Moreover, assume that the
noises $Z_n$ are uncorrelated and identically distributed with a
distribution with a density for which the Fisher information exits. Let
$\psi(x)$ and $\chi(x)$ be defined as in
Theorem~\ref{corollary:polyak-juditsky}-(iii) and satisfy the conditions
there. Assume in addition that $\chi(0)>0$, condition
\eqref{eqn:local-hessian-psi} with $\lambda = 1$, and there exits $K_3$ such
that
\begin{equation*}
\ex{  | \varphi(x+Z_1) |^4 } \leq K_3(1+|x|^4). 
\end{equation*}
Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
\begin{equation*}
V_n \triangleq \ex{ \left(\bar{U}_n-x^\star \right)^2 } = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
\end{equation*}
\end{thm}

@@

The regularity result~\eqref{eq:normal_expansion_lem} gives
\begin{equation*}
  \sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}}
  \sum_{i = 1}^n  \frac{\varphi(Z_i)}{\psi'(0)} + o_{P,n}(1).
\end{equation*}
The conditions in
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam} imply
that the Fisher information $I_h =
\E_h[\score_h(Z)^2]$ exists and is continuous for
$\score_h(z) = \frac{p'(z - h)}{f(z - h)}$,
and the asymptotic expansion~\eqref{eqn:lan-from-qmd}
with the preceding display give the joint convergence
\begin{equation*}
  \left(\sqrt{n} \bar{\Delta}_n, \log \frac{P^n_{h_n/\sqrt{n}}}{P^n_0}(Z_1^n)
  \right)
  \cd \normal \left( \left(0,-\frac{h^2}{2} I_0 \right),
  \begin{pmatrix}
    \frac{\chi(0)}{\psi'(0)^2} & \frac{-h}{ \psi'(0)}
    \E_p[\varphi(Z) \score_0(Z)] \\
    \frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
    & h^2 I_0
  \end{pmatrix}  \right).
\end{equation*}
Le Cam's third lemma \cite[Exm. 6.7]{VanDerVaart98} then implies the
convergence
\begin{equation*}
  \sqrt{n}\bar{\Delta}_n
  \mathop{\cd}_{P_{h_n/\sqrt{n}}^n}
  \Ncal\left(\frac{-h}{ \psi'(0)} \E_f[\varphi(Z) \score(Z)],
  \frac{\chi(0)}{\psi'(0)^2} \right)
\end{equation*}
under the alternatives $P_{h_n/\sqrt{n}}$, which gives
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}.

All that remains is to return to our proof of Lemma~\ref{lemma:qmd}:

>>>>

This proof requires somewhat more techinicality than the first part of the
theorem, including a brief detour into local asymptotic normality theory,
regular estimators, and quadratic-mean
differentiability~\cite[cf.]{VanDerVaart98}.
We assume without loss of generality that the median of the density
$f$ is 0, so that if $P_\theta$ has density $f(\cdot - \theta)$, the
median of $P_\theta$ is $\theta$.
We begin by recalling the statistical concepts we require.
\begin{definition}
  \label{definition:regular-estimator}
  A sequence of estimators $T_n$ for a parameter $\theta$ in the parametric
  family $\{P_\theta\}_{\theta \in \Theta}$ is \emph{regular at $\theta$} if
  there exists a distribution $Q$ such that for all bounded sequence
  $h_n$,
  \begin{equation*}
    \sqrt{n}(T_n - (\theta + h_n / \sqrt{n}))
    \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}}
    Q.
  \end{equation*}
\end{definition}
\begin{definition}
  \label{definition:qmd}
  Let $\{P_\theta\}_{\theta \in \Theta}$ have densities $p_\theta$
  with respect to a base measure $\mu$. The family
  is \emph{quadratic mean differentiable} (QMD) at
  $\theta$ with score $\score_\theta$ if
  \begin{equation}
    \label{eqn:qmd}
    \int \left(\sqrt{p_{\theta + h}} - \sqrt{p_\theta}
    - \half h^\top \score_\theta\sqrt{p_\theta} \right)^2 d\mu
    = o(\norm{h}^2)
  \end{equation}
  as $h \to 0$.
\end{definition}
\begin{definition}
  \label{definition:lan}
  A family of distributions $\{P_\theta\}_{\theta \in \Theta}$ is
  \emph{locally asymptotically normal with information matrix $I_\theta$} (LAN)
  at
  $\theta$ if there exists a sequence of random vectors $Z_n$ such that for
  all $h_n \to h$,
  \begin{equation*}
    \sum_{i = 1}^n \log \frac{dP_{\theta + h_n/\sqrt{n}}}{dP_\theta}
    (X_1, \ldots, X_n)
    = h^\top Z_n - \half h^\top I_\theta h + o_P(1)
  \end{equation*}
  where $Z_n \cd \normal(0, I_\theta)$ under $P_\theta$, where
  $X_i \simiid P_\theta$.
\end{definition}

These three definitions are linked in our case by a few important results.
First~\cite[Theorem 7.2]{VanDerVaart98}, if $\{P_\theta\}$ is QMD
(Def.~\ref{definition:qmd}) at the point $\theta$, then it is locally
asymptotically normal with $Z_n = \frac{1}{\sqrt{n}} \sum_{i = 1}^n
\score_\theta(X_i)$ and information matrix $I_\theta =
\E_\theta[\score_\theta \score_\theta^\top]$. Moreover, in any family
$\{P_\theta\}$ that is LAN (Def.~\ref{definition:lan}) at $\theta$, if $T_n$
is a regular estimator (Def.~\ref{definition:regular-estimator}) at $\theta$
with limiting distribution $Q$, then for any bounded, symmetric,
quasi-convex loss $L$ and $c < \infty$,
\begin{equation}
  \label{eqn:limit-law-regular}
  \limsup_n \sup_{\norm{h} \le c}
  \E_{P_{\theta + h/\sqrt{n}}}
  \left[L(\sqrt{n}(T_n - \theta - h / \sqrt{n}))\right]
  = \E[L(W)] ~~ \mbox{for~}W \sim Q
\end{equation}
(see Beran~\cite{beran1995role}, Eq.~(4.2)).
%
Thus, we show two results: first, that
that the family $\{P_\theta\}$ of distributions
defined by the shifted densities $\{f(\cdot - \theta)\}_{\theta \in \R}$
is quadratic-mean-differentiable at any $\theta$,
and second, that $\bar{\theta}_n$ is regular and
asymptotically normal.
The combination evidently gives the theorem.

For quadratic mean differentiability, we have the following lemma, somewhat
more general than we need; we defer proof to Sec.~\ref{sec:proof-qmd}.
\begin{lemma}[Extension of \cite{VanDerVaart98}, Lemma 7.6]
  \label{lemma:qmd}
  Let $p_\theta$ be a density with respect to $\mu$,
  and assume that $\theta \mapsto s_\theta(x) \defeq \sqrt{p_\theta(x)}$
  is absolutely continuous for all $x$. Let
  $\dot{p}_\theta(x) = \nabla_\theta p_\theta(x)$ (when it exists),
  and assume that
  \begin{equation*}
    \mu(\{x : \dot{p}_\theta(x) ~ \mbox{fails~to~exist}\}) = 0.
  \end{equation*}
  Assume that $I_\theta \defeq \E_{P_\theta}[\dot{p}_\theta
    \dot{p}_\theta^\top / p_\theta^2]$ is continuous at $\theta_0$. Then
  $P_\theta$ is QMD (Definition~\ref{definition:qmd}) at $\theta = \theta_0$
  with $\score_\theta = \dot{p}_\theta / p_\theta$.
\end{lemma}

By the assumption in Theorem~\ref{thm:sgd} that the density $f$
is Lipschitz continuous, we see that the location family
$\{P_\theta\}_{\theta \in \R}$ defined by $dP_\theta(x) = f(x - \theta)$
satisfies the conditions of Lemma~\ref{lemma:qmd}.

It remains to show that the average $\bar{\theta}_n$ is regular:
\begin{lemma}
  \label{lemma:sgd-median-regular}
  Let $h_n \to h \in \R$, and define $P_n = P_{\theta + h_n / \sqrt{n}}^n$.
  Then $\bar{\theta}_n$ is regular with
  \begin{align}
    \label{eqn:sgd-median-regular}
    \sqrt{n}\left( \bar{\theta}_n - \theta\right)
    \mathop{\cd}_{P_n}
    \normal\left( h,\frac{1}{4 f(0)^2}\right).
  \end{align}
\end{lemma}
\begin{proof}
  To show the convergence~\eqref{eqn:sgd-median-regular} we use the
  following refinement of Corollary~\ref{corollary:polyak-juditsky}, which
  provides a generalized convergence result for iteratively defined
  $\theta_n$, and whose
  proof we defer to Section~\ref{proof:normal-expansion}.
  %
  \begin{corollary}
    \label{corollary:normal-expansion}
    Let the conditions of Corollary~\ref{corollary:polyak-juditsky} hold,
    meaning that $\theta_i = \theta_{i-1} + \gamma_i \varphi(X_i -
    \theta_{i-1})$ for $X_i = \theta + Z_i$, where $Z_i$ are i.i.d.\ with
    $\E[\varphi(Z)] = 0$. Additionally assume the local smoothness
    condition that there exist $0 < \lambda \le 1$ and $K < \infty$ such
    that
    \begin{equation}
      \label{eqn:additional-local-smooth}
      \E[|\varphi(x + Z) - \varphi(Z)|^2]
      \le K (|x|^\lambda + x^2).
    \end{equation}
    Set $\Delta_i = \theta_i - \theta$ and $\bar{\Delta}_i = \frac{1}{n}
    \sum_{i=1}^n \Delta_i$. Then
    \begin{enumerate}[(i)]
    \item \label{item:regularity}
      The sequence $\Delta_i$ is regular, that is,
      \begin{equation}
        \sqrt{n} \bar{\Delta}_n
        = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)
        + o_{P,n}(1).
        \label{eq:normal_expansion_lem}
      \end{equation}
    \item \label{item:apply-le-cam} Let $Z_i$ as in
      Corollary~\ref{corollary:polyak-juditsky} have absolutely continuous
      density $p$ with median $0$, define $\score_h(z) = \frac{p'(z - h)}{p(z
        - h)}$, and assume that $I_h \defeq \E_\theta[\score_h(Z)^2]$ is
      continuous in $h$ near 0.  Then for any converging sequence $h_n \to h$,
      \begin{equation*}
        \sqrt{n} \bar{\Delta}_n
        \mathop{\cd}_{P_{\theta + h_n/\sqrt{n}}^n}
        \normal\left( \frac{-h}{\psi'(0)} \E_p[\varphi(Z) \score_0(Z)],
        \frac{\chi(0)}{\psi'^2(0)} \right).
      \end{equation*}
    \end{enumerate}
  \end{corollary}

  We now verify that the setting of Theorem~\ref{thm:sgd}
  (and Lemma~\ref{lemma:sgd-median-regular}) satisfies the
  conditions of Corollary~\ref{corollary:polyak-juditsky}. First, we have
  the obvious fact that
  \begin{equation*}
    |\sgn(z) - \sgn(x + z)|
    \le 2 \cdot \indic{|x| \ge |z|}.
  \end{equation*}
  Recalling that the density $f$ is Lipschitz with median 0,
  for $\varphi(z) = \sgn(z)$, and $Z = X - \theta$ distributed with
  density $f$, we have
  \begin{align*}
    \ex{ \left| \varphi(Z) - \varphi(x + Z) \right| }
    \leq 2 \Prob\left( |Z_1| \le |x|  \right)
    = 2 \int_{-|x|}^{|x|} f(t) dt
    = 4 f(0)|x| \pm 2 \int_{-|x|}^{|x|}
    \lip(f) t dt
    = 4 f(0) |x| + 2 \lip(f) x^2
  \end{align*}
  where $\lip(f)$ is the Lipschitz constant of $f$.
  For large $x$ we always have
  $\E[|\varphi(Z) - \varphi(x + Z)|] \le 2$, so that
  condition~\eqref{eqn:additional-local-smooth} holds.
  In addition, we have
  \begin{equation*}
    \int_{\R} \varphi(x) f'(x ) dx
    = \int_{\R} \sgn(x) f'(x ) dx =
    \int_0^\infty f'(x ) dx
    - \int_{-\infty}^0 f'(x )
    = -2 f(0) = -\psi'(0).
  \end{equation*}
  Corollary~\ref{corollary:normal-expansion}
  now implies the convergence \eqref{eqn:sgd-median-regular}.
\end{proof}

Combining Lemmas~\ref{lemma:qmd} and~\ref{lemma:sgd-median-regular}
with the limit~\eqref{eqn:limit-law-regular} gives
Theorem~\ref{thm:sgd}\eqref{item:sgd-regular}.

\subsubsection*{Proof of Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}}

We begin with the following result from \cite{polyak1990new}:
\begin{corollary}[\cite{polyak1990new}, Theorem 2]
  \label{corollary:polyak-mse}
  Let
  \begin{align} \label{eq:polyak_new_measurements}
    \begin{cases}
      U_n = U_{n-1} - \gamma_n \varphi(Y_n), & Y_n = g'(U_{n-1})+Z_n \\
      \bar{U}_n= \frac{1}{n} \sum_{i=1}^n U_n, & n=1,2,\ldots.
    \end{cases}
  \end{align}
  Assume that the function $g(x)$ is twice differentiable with a strictly
  positive and uniformly bounded second derivative. In particular, $g(x)$ is
  convex with a unique minimizer $x^\star \in \R$. Moreover, assume that the
  noises $Z_n$ are uncorrelated and identically distributed with a
  distribution with a density for which the Fisher information exits. Let
  $\psi(x)$ and $\chi(x)$ be defined as in
  Theorem~\ref{corollary:polyak-juditsky}-(iii) and satisfy the conditions
  there. Assume in addition that $\chi(0)>0$, condition
  \eqref{eqn:local-hessian-psi} with $\lambda = 1$, and there exits $K_3$ such
  that
  \begin{equation*}
    \ex{  | \varphi(x+Z_1) |^4 } \leq K_3(1+|x|^4). 
  \end{equation*}
  Finally, assume that the sequence $\{\gamma_n \}$ satisfies conditions \eqref{eq:conditions1} and \eqref{eq:conditions2}. Then
  \begin{equation*}
    V_n \triangleq \ex{ \left(\bar{U}_n-x^\star \right)^2 } = n^{-1}\frac{\chi(0)} { (\psi'(0))^2 (g''(x^\star))^2 } + o(n^{-1}).
  \end{equation*}
\end{corollary}

@@

The regularity result~\eqref{eq:normal_expansion_lem} gives
\begin{equation*}
  \sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}}
  \sum_{i = 1}^n  \frac{\varphi(Z_i)}{\psi'(0)} + o_{P,n}(1).
\end{equation*}
The conditions in
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam} imply
that the Fisher information $I_h =
\E_h[\score_h(Z)^2]$ exists and is continuous for
$\score_h(z) = \frac{p'(z - h)}{p(z - h)}$,
and the asymptotic expansion~\eqref{eqn:lan-from-qmd}
with the preceding display give the joint convergence
\begin{equation*}
  \left(\sqrt{n} \bar{\Delta}_n, \log \frac{P^n_{h_n/\sqrt{n}}}{P^n_0}(Z_1^n)
  \right)
  \cd \normal \left( \left(0,-\frac{h^2}{2} I_0 \right),
  \begin{pmatrix}
    \frac{\chi(0)}{\psi'(0)^2} & \frac{-h}{ \psi'(0)}
    \E_p[\varphi(Z) \score_0(Z)] \\
    \frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
    & h^2 I_0
  \end{pmatrix}  \right).
\end{equation*}
Le Cam's third lemma \cite[Exm. 6.7]{VanDerVaart98} then implies the
convergence
\begin{equation*}
  \sqrt{n}\bar{\Delta}_n
  \mathop{\cd}_{P_{h_n/\sqrt{n}}^n}
  \Ncal\left(\frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score(Z)],
  \frac{\chi(0)}{\psi'(0)^2} \right)
\end{equation*}
under the alternatives $P_{h_n/\sqrt{n}}$, which gives
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}.
